---
title: "Cyclistic_plotly"
author: "Corey Neff"
date: "7/5/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions 

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

## Loading the data

Here I am, again, loading the "Cyclistic" dataset provided by Google. It is 12 separate CSVs, one for each month, containing geocoded data for bike-share usage in Chicago. For the Plotly visualizations, I will be using the **ggplotly()** function as it is easier to work with ggplot2.


```{r data, warning = F}
librarian::shelf(dplyr, purrr, data.table, lubridate, ggplot2, plotly)

mydata <- do.call(rbind, lapply(list.files(pattern="*.csv"), fread))


mydata <- mydata %>% 
      select(-c(ride_id, start_station_name, end_station_name)) %>%
      mutate(ride_length = as.numeric(ended_at-started_at),
             ended_at = ymd_hms(ended_at),
             started_at = ymd_hms(started_at),
             day = factor(weekdays(started_at), c("Monday", "Tuesday", "Wednesday", "Thursday","Friday", "Saturday", "Sunday")),
             member_casual = as.factor(stringr::str_to_title(member_casual)))

mydata$ride_length <- replace(mydata$ride_length, which(mydata$ride_length < 0), NA)

summary(mydata)

```

## First Plot: Ride_length

This graph shows a histogram of ride length in seconds with respect to the member category. As you can see, non-members ("casual") tend to ride for a longer length of time.

```{r Ride_length, warning=F, message=F}
ggplotly(
   ggplot(data = mydata) +
      geom_histogram(aes(x=ride_length, fill = member_casual))+
      xlim(0,5000) +
      labs(fill = "Casual User or Member?") +
      xlab("Ride Length (s)") +
      ggtitle(("Histogram of Ride Length by Member Status")) +
      theme_bw()
)
```

## Second Plot: Day of the week

This graph shows the dsitribution of the average # of rides per day of the week with respect to the member category. As you can see, member bike usage is less dependent of the day, while non-member usage is focused on the weekends.

```{r Day, warning = F, message=F}

ggplotly(
   ggplot(mydata) +
      geom_bar(aes(x=day, fill = member_casual), position = 'dodge')+
      labs(fill = "Casual User or Member?") +            
      xlab("Day of the Week") +
      ggtitle(("Frequencies of Weekday Usage by Member Status")) +
      theme_bw()
)