---
title: "App Pitch"
author: "Corey Neff"
date: "7/8/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Instructions

This simple RMarkdown presentatio was created as the final assignment for the Creating Data Products Coursera course. Here I will be pitching the app I created, which can be found [HERE](https://nebuchadnezz.shinyapps.io/Cyclistic_App/).

**Requirements:**

- It must be done in Slidify or Rstudio Presenter

- It must be 5 pages

- It must be hosted on github or Rpubs

- It must contained some embedded R code that gets run when slidifying the document

## The Problem

*Cyclistic* is a fictional bike-sharing company based in Chicago, IL, and they have one question: 

- How do members differ from non-members in their usage of the bikes?

To answer this question, a number of visuals (including both graphs and a map) were created to show how members and casual users differ.

## Sample Graph

```{r sample, message=F, warning = F}


library(librarian)
shelf(dplyr, ggplot2, plotly)
set.seed(69)

mydata <- readRDS(file = "data.rds")
ggplotly(ggplot(mydata) +
            geom_histogram(aes(x=ride_length, fill = member_casual)) +
            xlim(0, 10000) +
            labs(fill = "Member Status?") +            
            xlab("Length of Time (s)") +
            ggtitle(paste("Distribution of","Length of Time (s)"," by Member Status")) +
            theme_bw())
```

## The App

Here, the second tab of the app can be found. To use the app, please visit the webpage listed earlier.

```{r APP, echo = F, message=F, warning = F}

library(librarian)
shelf(dplyr, ggplot2, plotly, leaflet, shiny)
set.seed(69)

mydata <- readRDS(file = "data.rds")

shinyApp(

ui <- fluidPage(theme = shinythemes::shinytheme("yeti"),
    navbarPage(
        title = "Google's Cyclistic Data Shiny App",
        theme = shinythemes::shinytheme("yeti"),
        
        tabPanel("Plots",
                 sidebarPanel(
                     tags$h3("Which variable?"),
                     selectInput("variable_cont", "Choices (continuous):",
                                 choices = list("Ride Length (s)" = "length",
                                                "Ride Distance (m) " = "dist"
                                 )),
                     selectInput("variable_cat", "Choices (discrete):",
                                 choices = list("Day of the Week" = "weekday",
                                                "Type of Bike" = "type"
                                 ))
                 ), 
                 mainPanel(
                     plotly::plotlyOutput("plot1", width = "90%"),
                     plotly::plotlyOutput("plot2", width = "90%")
                 ) 
                 
        )
    ) 
), 

server <- function(input, output, session) {
    
output$plot1 <- renderPlotly(
    
    if(input$variable_cont == "length"){
ggplotly(ggplot(mydata) +
            geom_histogram(aes(x=ride_length, fill = member_casual)) +
            xlim(0, 10000) +
            labs(fill = "Member Status?") +            
            xlab("Length of Time (s)") +
            ggtitle(paste("Distribution of","Length of Time (s)"," by Member Status")) +
            theme_bw())
    }
    else{
ggplotly(ggplot(mydata) +
            geom_histogram(aes(x=distance, fill = member_casual)) +
            xlim(0, 10000) +
            labs(fill = "Member Status?") +            
            xlab("Distance (m)") +
            ggtitle(paste("Distribution of ","Distance (m)","by Member Status")) +
            theme_bw())
    }           
)

output$plot2 <- renderPlotly(     
    
    if(input$variable_cat== "weekday"){
        
    ggplotly(ggplot(mydata) +
        geom_bar(aes(x=day, fill = member_casual), position = "dodge") +
        labs(fill = "Member Status?") +            
        xlab("Day of the Week") +
        ggtitle(paste("Distribution of","Weekday Usage"," by Member Status")) +
        theme_bw())
    }
    else{
        ggplotly(ggplot(mydata) +
            geom_bar(aes(x=rideable_type, fill = member_casual), position = "dodge") +
            labs(fill = "Member Status?") +            
            xlab("Rideable Type") +
            ggtitle(paste("Distribution of","Rideable Type"," by Member Status")) +
            theme_bw())
    }
)
},   options = list(height = 200)
)
```